phRAIDER: Pattern-Hunter based Rapid Ad Initio \\ Identification of Elemenrary Repeats

### 2015-09-18 manuscript/JCB/manuscript.tex
Updating manuscript.txt

\documentclass[10pt]{article}
\usepackage{longtable}
\usepackage{ulem}
\usepackage{authblk}
\usepackage{algorithmic}
\def\includegraphic{}
\def\includegraphics{}
\pagestyle{myheadings}

@@

@@

\begin{algorithmic}
\If {$i\geq maxval$}
    \State $i\gets 0$
\Else
    \If {$i+k\leq maxval$}
        \State $i\gets i+k$
    \EndIf
\EndIf
\end{algorithmic}

>>>>

\documentclass[10pt]{article}
\usepackage{longtable}
\usepackage{ulem}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{algorithmicx}
\usepackage{color}
\def\includegraphic{}
\def\includegraphics{}
\pagestyle{myheadings}

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\cyan}[1]{{\color{cyan}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}

@@

\newcommand{\comment}[1]{\State \red{\# #1}}

@@

\begin{algorithm}
\begin{algorithmic}
  \Function{phRAIDER}{Genome $G$, Seed $s$, MinFrequence $f$}
    \State Queue$<$Family$>$ $Q$;

    \State \Comment{Iterate over all $l$-mer positions in $G$}
    \For {$i \leftarrow 1 \to |G|-|s|$}

       \comment{Remove and families whose last $l$-mer did not occur in the last $i$}
       \comment{bases (hence must be closd out).}
       \While{$i - $location($Q$, finish, last, end)$ > |s|$}
         \State $Q.$dequeue()
       \EndWhile
       \State
       \comment{Get the $l$-mer occuring at $G_i$ and remove letters corresponding to $0$s in $s4$.}
       \State $v \leftarrow \mbox{seeded}(G[i],x)$ 
       \State
       \comment{Add to list of $v$'s positions.}
       \State $H[v].push(i)$
       \State
       \If {$|H|(v)| == 2$}
          \comment{$v$ either is the beginning of a family, or should be combined}
          \comment{with a previous $l$-mer to form a family.}
          \State $F = \mbox{arg\_find}_{F \in Q}\{$loc($v$, start, first) - loc($f$, start, first, begin) $==i - $loc($f$, start last end)$\}$
          \If {$F$}
             $Q.$requeue($F$)
          \EndIf
          \State last($Q$).addLmer($v$)   
       \ElsIf {$|H[v]| > 2$}
          \comment{Is $v$ the proper continuation of a family, or does it}
          \comment{need to be split off?}
          \State $F \leftarrow v.$family()
          \If {$f \not\in Q$}
              \comment{$v$ belongs to a family whose last instance is too far away.}
              \If {$v \neq F.first()$}
                  \comment{$v$ is not the first $l$-mer of its family
                  $F' \leftarrow F.$split($F.$v$)
              \Else
                  $F' \leftarrow F.$split($F.$lastSeen())
              \EndIf
              \State $Q.$enqueue($F'$)
          \Else
              \If {$v == F.$first()}
                 \comment{$v$ is the first $l$-mer of $F$, so $F$ is moved to the back of $Q$}
                 $Q$.requeue($F$)
              \ElsIf {$F.$lastSeen()$.$next$==v$}
                 ???
                 $F.$setLastSeen($v$)
              \EndIf
           \EndIf                             
       \EndIf
       \EndFor
       \State tieLooseEnds()
  \EndFunction
\end{algorithmic}
\end{algorithm}
